On The Difficulty of Computing Non-Commutative Signature Gröbner Bases

### 2022-01-26 article_issac.tex

Looking at principal syzygies and the algorithm for computing new ones, we wonder if an automaton can recognize leading monomials of syzygies in the case where the Gröbner basis is finite. Let us show that this is not the case using the non regular language\linebreak $\{a^nb^n \;|\; n \in \N\}$. Let us consider the alphabet 
$$\{a, b, c, d, e, s, t, x, y, z, \infty\}$$
and polynomials
\fixmecc{s -S ss partout}
\begin{align*}
g_1 & := sa - tcx \\
g_2 & := xa - ax \\
g_3 & := xd - dx \\
g_4 & := ya - ay \\
g_5 & := yd - dy \\
g_6 & := xbb - dyb \\
g_7 & := cya - ccx \\
g_8 & := xbe - dze \\
g_9 & := dz - zb \\
g_{10} & := cz - za \\
g_{11} & := s-tz
\end{align*}
together with the order $m_1 < m_2$ if:
\fixmecc{on compare d'abord par degrés}
\begin{itemize}
\item there are less $\infty$ symbols in $m_1$ than in $m_2$,
\item $m_1$ and $m_2$ have the same number of $\infty$ symbols and there are less $s$ symbols in $m_1$ than in $m_2$,
\item $m_1$ and $m_2$ have the same numbers of $\infty$ and $s$ symbols, but
$m_1 <_{deglex} m_2$ where\\ $a < b < c < d < x < y < z < e < t < s < \infty$.
\end{itemize}

\fixmecc{dire que cet ordre est fair}

\fixmecc{Given $l,r,l',r'\in\KX$, have (let?) $l\varepsilon_i r\leq l'\varepsilon_j r'$ if
  \begin{itemize}
  \item $l\LM(g_i)r < l'\LM(g_j)r'$
  \item $l\LM(g_i)r = l'\LM(g_j)r'$ et $i < j$
  \item $l\LM(g_i)r = l'\LM(g_j)r'$ et $i = j$ et $\deg{l} < \deg{l'}$.
  \end{itemize}
      {\bf dire que l'ordre est fair}

>>>>

Looking at principal syzygies and the algorithm for computing new ones, we wonder if an automaton can recognize leading monomials of syzygies in the case where the Gröbner basis is finite. Let us show that this is not the case using the non regular language\linebreak $\{a^nb^n \;|\; n \in \N\}$. Let us consider the alphabet 
$$\{a, b, c, d, e, s, t, x, y, z, \infty\}$$
and polynomials
\begin{align*}
g_1 & := ssa - tcx \\
g_2 & := xa - ax \\
g_3 & := xd - dx \\
g_4 & := ya - ay \\
g_5 & := yd - dy \\
g_6 & := xbb - dyb \\
g_7 & := cya - ccx \\
g_8 & := xbe - dze \\
g_9 & := dz - zb \\
g_{10} & := cz - za \\
g_{11} & := ss-tz
\end{align*}
together with the order $m_1 < m_2$ if:
\begin{itemize}
\item the degree of $m_1$ is strictly smaller than the degree of $m_2$,
\item $m_1$ and $m_2$ have the same degree and there are less $\infty$ symbols in $m_1$ than in $m_2$,
\item $m_1$ and $m_2$ have the same degree, the same number of $\infty$ symbols and there are less $s$ symbols in $m_1$ than in $m_2$,
\item $m_1$ and $m_2$ have the same degree, the same numbers of $\infty$, and the same number $s$ symbols, but
$m_1 <_{lex} m_2$ where\\ $a < b < c < d < x < y < z < e < t < s < \infty$.
\end{itemize}
Such defined, this order is fair.

\fixmecc{Given $l,r,l',r'\in\KX$, have (let?) $l\varepsilon_i r\leq l'\varepsilon_j r'$ if
  \begin{itemize}
  \item $l\LM(g_i)r < l'\LM(g_j)r'$
  \item $l\LM(g_i)r = l'\LM(g_j)r'$ et $i < j$
  \item $l\LM(g_i)r = l'\LM(g_j)r'$ et $i = j$ et $\deg{l} < \deg{l'}$.
  \end{itemize}
  Such defined this order is fair.
